---
title: "WriteUp Linear Model with prediction"
author: "Galilea Hernandez"
date: "11/02/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

## Model 1: SIMS~ARM
### Scartter Plot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```


```{r}
basicNN + geom_point() + ggtitle("SIMS~ARM")
```

The graph shows us that the simulation arm strength is in between 50 - 100.

### Numerical Results  

```{r}
cor(SIMS~ARM,data=data)
```

the numerical data shows us that there is a positive value between the simulated arm strength of the individuals. The value supports the graph data of the SIMS and ARMS comparison.

### Inferential Results 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```


The inferential data shows us a positive value for SIMS and ARM with an equation for the slope of 0.054563x-4.095160.

### Create target

```{r}
target<-data.frame(ARM=90, GRIP=90)
```

### Prediction of Model 1

```{r}
predict(model.1,target,interval=c("prediction"))
```

The prediction shows that the fit of the plot is 0.8155096 but 95% of the time, we are going to have a value between -1.617843 and 3.248863.

### Scartter plot for Model 1 with linear fit

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))

```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)

```


THe graph shows us the expected results for SIMS~ARM. We see that the line interjects across the midpoint in a positive direction.


## Model 2: SIMS~GRIP

### Scartter Plot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))

```

```{r}
basicNN + geom_point() + ggtitle("SIMS~GRIP")

```


The graph shows us that the simulated grip strength lies within 100-150.

### Numerical Results

```{r}
cor(SIMS~GRIP,data=data)
```


The numerical results show us that the SIMS~GRIP value is lower than the SIMS~ARM correlation value with was 0.6398458 which tells us that SIMS~ARM has a better fit than Sims vs Grip. Sims~Arm we got 0.6860073. 


### Inferential Results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

The inferential results give us an equation of 0.045463x-4.809675 as the equation for our line of best fit. With the positive coefficient we have a positive slope.

### Prediction of Model 2

```{r}
predict(model.2,target,interval=c("prediction"))
```

The table shows that our best fit value for this scenario is -0.7180063, but 95% of the time the value will be between -3.292089 and 1.856077.

### Scatter plot for Model 2 with linear fit

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))

```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)
```

The scatter plots of SIMS~ARM and SIMS~GRIP, tells us that the data in model 1 is more scattered across the ends of the best fit line however on Model 2  we have less data point towards the ends of the best fit line.


## Model 3: SIMS~ARM+GRIP

### Numerical Results

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation value for model 3 came out to be higher than model 1 and 2. The value above tells us that we have a 0.7326545 correlation between Sims vs Arm+Grip. This gives us a higher value from the Sims vs Arm and Sims vs Grip. It shows that the most accurate model would be when looking at both the Arm and Grip data together rather than comparing them individually against Sims.


### Inferential Results

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

model.3=(-5.433871+0.037311*ARM+0.024471*GRIP)

This data gives us an equation of SIMS= 0.037311xARM + 0.024470xGRIP -5.433871 for what would be the best fit model. 







