---
title: "WriteUp Linear Model with prediction"
author: "Galilea Hernandez"
date: "11/02/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

## Model 1: SIMS~ARM
### Scartter Plot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```


```{r}
basicNN + geom_point() + ggtitle("SIMS~ARM")
```

The graph shows us that the simulation arm strength is in between 50 - 100.

### Numerical Results  

```{r}
cor(SIMS~ARM,data=data)
```

the numerical data shows us that there is a positive value between the simulated arm strength of the individuals. The value supports the graph data of the SIMS and ARMS comparison.

### Inferential Results 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```


The inferential data shows us a positive value for SIMS and ARM with an equation for the slope of 0.054563x-4.095160.

### Create target

```{r}
target<-data.frame(ARM=90, GRIP=90)
```

### Prediction of Model 1

```{r}
predict(model.1,target,interval=c("prediction"))
```

The prediction shows that the fit of the plot is 0.8155096 but 95% of the time, we are going to have a value between -1.617843 and 3.248863.

### Scartter plot for Model 1 with linear fit

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))

```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)

```


THe graph shows us the expected results for SIMS~ARM. We see that the line interjects across the midpoint in a positive direction.


## Model 2: SIMS~GRIP

### Scartter Plot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))

```

```{r}
basicNN + geom_point() + ggtitle("SIMS~GRIP")

```


The graph shows us that the simulated grip strength lies within 100-150.

### Numerical Results

```{r}
cor(SIMS~GRIP,data=data)
```


The numerical results show us that the SIMS~GRIP value is lower than the SIMS~ARM correlation value with was 0.6398458 which tells us that SIMS~ARM has a better fit than Sims vs Grip. Sims~Arm we got 0.6860073. 


### Inferential Results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

The inferential results give us an equation of 0.045463x-4.809675 as the equation for our line of best fit. With the positive coefficient we have a positive slope.

### Prediction of Model 2

```{r}
predict(model.2,target,interval=c("prediction"))
```

The table shows that our best fit value for this scenario is -0.7180063, but 95% of the time the value will be between -3.292089 and 1.856077.

### Scatter plot for Model 2 with linear fit

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))

```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)
```

The scatter plots of SIMS~ARM and SIMS~GRIP, tells us that the data in model 1 is more scattered across the ends of the best fit line however on Model 2  we have less data point towards the ends of the best fit line.


## Model 3: SIMS~ARM+GRIP

### Numerical Results

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation value for model 3 came out to be higher than model 1 and 2. The value above tells us that we have a 0.7326545 correlation between Sims vs Arm+Grip. This gives us a higher value from the Sims vs Arm and Sims vs Grip. It shows that the most accurate model would be when looking at both the Arm and Grip data together rather than comparing them individually against Sims.


### Inferential Results

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

model.3=(-5.433871+0.037311*ARM+0.024471*GRIP)

This data gives us an equation of SIMS= 0.037311xARM + 0.024470xGRIP -5.433871 for what would be the best fit model. 

### Prediction for Model 3

```{r}
predict(model.3,target,interval=c("prediction"))

```

The table above gives us a value of 0.1263886 as the target point for Sims vs Arm+Grip. With a 95% interval the value will be between -2.1626 and 2.415377.

### Comparing Models Using anova.

#### Model 1 vs Model 3

```{r}
anova(model.1,model.3)
```

The P-value when comparing Model 1 vs Model 3 is 0.000004994. This tells us that Model 3 is better than model 1 as we know that model one is already listed in model 3.
From the data above, we can see that model 3 was more accurate than model 1, if there were to be no differences between the two models, we would have a 0.000004994% chance of this being the outcome. Looking at the data we had 145 degree of freedom for the model.1 and 144 for the model.3. In the residual sum of square values, we have 217.88 errors for model.1 and 188.43 errors for model.3. This shows that the plots for the Arm+Grip was more accurate by 29.45 points.  


#### Model 2 vs Model 3

```{r}
anova(model.2,model.3)
```

The p-value between model 2 and model 3 is 0.000000001495. This value tells us that Arm vs Grip is giving more data than Arm vs Sims. This value tells us that Model 3 is much better than Model 2 and model 3 already includes model 2 data. 
From the data table, we are able to see that in this case model 3 was more accurate than model 2. If there were to be no differences between the two models, we would have a 0.000000001495% chance of getting these exact results. The difference in degrees of freedom is 1 since model 2 had 145 and model 3 had 144. The residual sum of squares for each model is 243.07 for model 2 and 188.43 for model 3. This gives us a difference of 54.639 errors making the model 3 more accurate than the model 2. 

#### Model 1 vs Model 2 


```{r}
anova(model.1,model.2)
```

From this data model 1 has a residual sum of squares of 217.88 and model 2 has 243.07. This gave us a difference of -25.189 which shows us that the model 1 is a more accurate model when comparing Sims to Arm and Grip individually.

## Discussion and Conclusion
We created models to compare more than one numerical-numerical value at once and analyzed the probability and preciseness of the values that we gathered.
The P-value when comparing Model 1 vs Model 3 is 0.000004994. This tells us that Model 3 is better than model 1 as we know that model one is already listed in model 3. The p-value for this comparison between model 2 and model 3 is 0.000000001495. This value tells us that Arm vs Grip is giving more data than Arm vs Sims. Also this value tells us that Model 3 is much better than Model 2 and model 3 already includes model 2 data. 

 



