---
title: "WriteUp Linear Model with prediction"
author: "Galilea Hernandez"
date: "11/02/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

## Model 1: SIMS~ARM
### Scartter Plot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```


```{r}
basicNN + geom_point() + ggtitle("SIMS~ARM")
```

The graph shows us that the simulation arm strength is in between 50 - 100.

### Numerical Results  

```{r}
cor(SIMS~ARM,data=data)
```

the numerical data shows us that there is a positive value between the simulated arm strength of the individuals. The value supports the graph data of the SIMS and ARMS comparison.

### Inferential Results 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```


The inferential data shows us a positive value for SIMS and ARM with an equation for the slope of 0.054563x-4.095160.

### Create target

```{r}
target<-data.frame(ARM=90, GRIP=90)
```






