---
title: "WriteUp Linear Model with prediction"
author: "Galilea Hernandez"
date: "11/02/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

## Model 1: SIMS~ARM
### Scartter Plot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```


```{r}
basicNN + geom_point() + ggtitle("SIMS~ARM")
```

The graph shows us that the simulation arm strength is in between 50 - 100.

### Numerical Results  

```{r}
cor(SIMS~ARM,data=data)
```

the numerical data shows us that there is a positive value between the simulated arm strength of the individuals. The value supports the graph data of the SIMS and ARMS comparison.

### Inferential Results 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```


The inferential data shows us a positive value for SIMS and ARM with an equation for the slope of 0.054563x-4.095160.

### Create target

```{r}
target<-data.frame(ARM=90, GRIP=90)
```

### Prediction of Model 1

```{r}
predict(model.1,target,interval=c("prediction"))
```

The prediction shows that the fit of the plot is 10.8155096 but 95% of the time, we are going to have a value between -1.617843 and 3.248863.

### Scartter plot for Model 1 with linear fit

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))

```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)

```


THe graph shows us the expected results for SIMS~ARM. We see that the line interjects across the midpoint in a positive direction.


## Model 2: SIMS~GRIP

### Scartter Plot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))

```

```{r}
basicNN + geom_point() + ggtitle("SIMS~GRIP")

```


The graph shows us that the simulated grip strength lies within 100-150.

### Numerical Results

```{r}
cor(SIMS~GRIP,data=data)
```


The numerical results show us that the SIMS~GRIP value is lower than the SIMS~ARM correlation value with was 0.6398458 which tells us that SIMS~ARM has a better fit than Sims vs Grip. Sims~Arm we got 0.6860073. 




